\section{Conferences, Workshops, Schools and Talks}

\begin{cventries}
    \multiline{2021}{$32^{nd}$ Rencontres de Blois, France}{
        Invited presentation: Status of searches for dark matter at the LHC.
    }
    
    \multiline{2019}{ATLAS Exotic+HDBS workshop, Napoli, Italy}{
         Invited presentation: High mass resonances in hadronic final states: status and plan.
    }
    
    \multiline{2019}{Moriond QCD 2019,  La Thuile, Aosta Valley, Italy}{
        Invited presentation: Searches for New Resonances (lepton, jets) at ATLAS and CMS.
    }
    
    \singleline{2019}{ATLAS Standard Model workshop, LAL National Lab, France}
     \singleline{2016}{Summer School and Workshop on the Standard Model and Beyond, Corfu, Greece}
     \singleline{2016}{ATLAS SUSY workshop, Sussex, UK.}
     \singleline{2015}{Partikeldagarna national conference, Uppsala, Sweden.}
     \singleline{2015}{CERN HEP summer school, CERN, Geneva, Switzerland.}
     \singleline{2015}{Excellence in Detectors and Instrumentation Technologies (EDIT) school, INFN-LNF, Italy.}

     \multiline{2014}{ICHEP, Valencia, Spain}{
         Poster presentation: Search for direct top squark pair production in final states with one isolated lepton with the ATLAS detector.
     }

     \multiline{2014}{Partikeldagarna national conference, Växjö, Sweden.}{
         Presentation: Search for direct top squark pair production in final states with one isolated lepton with the ATLAS detector.
     }

     \singleline{2014}{ATLAS SUSY $^{3rd}$ generation squarks workshop, Milano, Italy.}

     \singleline{2012}{CHIPP PhD Winter School, Engelberg, Switzerland.}
     \singleline{2012}{Partikeldagarna national conference, Stockholm, Sweden.}



\end{cventries}
