\newpage

\section{Publications}

\begin{cventries}
    
\begin{itemize}
	\item \textbf{Paper} ATLAS Collaboration, Search for heavy particles in the $b$-tagged di-jet mass distribution with additional $b$-tagged jets in proton-proton collisions at $\sqrt{s}=13$ TeV with the ATLAS experiment, Phys. Rev. D 105, 012001 (2022).
	
	\item \textbf{Paper} ATLAS Collaboration, Search for new resonances in mass distributions of jet pairs using 139 fb$^{-1}$ of $pp$ collisions at $\sqrt{s}=13$ TeV with the ATLAS detector, JHEP 03 (2020) 145, 10.1007/JHEP03(2020)145.
	
	\item \textbf{paper} Y. Abulaiti, Search for new Resonances (lepton, jets) at ATLAS and CMS, Proceedings of the $54^{th}$ Rencontres de Moriond (2019) 133,  ATL-PHYS-PROC-2019-034.
	
	\item \textbf{paper} Y. Abulaiti, Search for top squark pair production in final states with one isolated lepton, jets, and missing transverse momentum in $\sqrt{s}=8$ TeV pp collisions with the {ATLAS} detector, Nuclear and Particle Physics Proceedings 273-275 (2016) 2415-2417.
	
	\item \textbf{Paper } ATLAS Collaboration, Search for top squarks in final states with one isolated lepton, jets, and missing transverse momentum in $\sqrt{s} = 13$ TeV pp collisions with the ATLAS detector, Phys.Rev. D94 (2016) no.5, 052009, DOI:10.1103/PhysRevD.94.052009.
	
	\item \textbf{Paper } ATLAS Collaboration, ATLAS Run 1 searches for direct pair production of $3^{rd}$ generation squarks at the Large Hadron Collider, Eur. Phys. J. C75 no. 10, (2015) 510, arXiv:1506.08616 [hep-ex].
	
	\item \textbf{Paper } ATLAS Collaboration, Search for top squark pair production in final states with one isolated lepton, jets,  and missing transverse momentum in $\sqrt{s}=8$~TeV pp collisions with the ATLAS detector, JHEP 1411 (2014) 118, DOI: 10.1007/JHEP11(2014)118.
	
	\item \textbf{Paper }ATLAS Collaboration, Summary of the ATLAS experiment's sensitivity to supersymmetry after LHC Run 1 interpreted in the phenomenological MSSM, JHEP 10 (2015) 134, arXiv:1508.06608 [hep-ex].
	
	\item \textbf{ATLAS-CONF} Search for top squarks in final states with one isolated lepton, jets, and missing transverse momentum in $\sqrt{s} = 13$ TeV pp collisions with ATLAS data, ATLAS-CONF-2016-050.
\end{itemize}

\end{cventries}
